Multipoint Approximation Method for Large Scale Design Optimization Problems Under Uncertainty

### 2017-12-12 2018/LION/LION2018.tex
references are updated

\bibliography{bibliography}{}
\bibliographystyle{nature}

>>>>

%\bibliography{bibliography}{}
%\bibliographystyle{nature}

\begin{thebibliography}{10}

\bibitem{RockafellarUryasev2000}
Rockafellar, R., Uryasev, S.:
\newblock Optimization of conditional value-at-risk.
\newblock The Journal of Risk \textbf{2}(3), 21--41 (2000)

\bibitem{SchillingsSchulz2015}
Schillings, C., Schulz, V.:
\newblock On the influence of robustness measures on shape optimization with stochastic uncertainties.
\newblock Optimization and Engineering \textbf{16}(2), 347--386 (2015)

\bibitem{Toropov1989}
Toropov, V.:
\newblock Simulation approach to structural optimization.
\newblock Structural Optimization \textbf{1}, 37--46 (1989)

\bibitem{Toropov1992}
Toropov, V.:
\newblock Multipoint approximation method in optimization problems with expensive function values.
\newblock In: Sydow, A. (ed.) Proceedings of the 4th international symposium on Systems analysis and simulation, 
pp. 207--212, Elsevier,  (1992)

\bibitem{ToropovFilatov1993}
Toropov, V., Filatov, A., Polynkin, A.:
\newblock Multiparameter structural optimization using fem and multipoint explicit approximations.
\newblock Structural Optimization \textbf{6}, 7--14 (1993)

\bibitem{ShahparPolynkinToropov2008}
Shahpar, S., Polynkin, A., Toropov, V.:
\newblock Large scale optimization of transonic axial compressor rotor blades.
\newblock In:  49th AIAA/ASME/ASCE/AHS/ASC Structures, Structural Dynamics, and Materials Conference, AIAA, art. no. 2008-2056
 (2008)

\bibitem{PolynkinToropovShahpar2008}
Polynkin, A., Toropov, V., Shahpar, S.:
\newblock Design optimization of aircraft engine components.
\newblock In: Proc. of 7th ASMO UK / ISSMO Conf. on Engineering Design Optimization. Process and Product Improvement (2008)

\bibitem{PolynkinToropovShahpar2010}
Polynkin, A., Toropov, V., Shahpar, S.:
\newblock Multidisciplinary optimization of turbomachinery based on metamodel built by genetic programming.
\newblock In: 13th AIAA/ISSMO Multidisciplinary Analysis and Optimization Conference (2010)

\bibitem{KeulenToropovMarkine1996}
van Keulen, F., Toropov, V., Markine, V.:
\newblock Recent refinements in the multi-point approximation method in conjunction with adaptive mesh refinement.
\newblock In: McCarthy, J.M. (ed.) Proc. of ASME Design Engineering Technical Conferences and Computers
  in Engineering Conf., 1--12, ASME, Irvine CA (1996)

\bibitem{ToropovKeulenMarkine1996}
Toropov, V., van Keulen, F., Markine, V., de~Boer, H.:
\newblock Refinements in the multi-point approximation method to reduce the effects of noisy responses.
\newblock In: 6th AIAA/NASA/ISSMO Symp. on Multidisciplinary Analysis and Optimization,  pp. 941--951, AIAA (1996)

\bibitem{ToropovMarkineHolden1999}
Toropov, V., Markine, V., Holden, C.:
\newblock Use of mid-range approximations for optimization problems with functions of domain-dependent calculability.
\newblock In: 3rd ISSMO/UBCAD/UB/AIAA World Congress of Structural and Multidisciplinary Optimization (1999).

\bibitem{ToropovMarkine1996}
Toropov, V., Markine, V.:
\newblock The use of simplified numerical models as mid-range approximations.
\newblock In: 6th AIAA/NASA/ISSMO Symp. on Multidisciplinary Analysis and Optimization, pp. 952--958 (1996).

\bibitem{ToropovAlvarez1998}
Toropov, V., Alvarez, L.:
\newblock Creation of multipoint approximations using genetic programming.
\newblock In: Parmee, I.C. (ed.) Adaptive Computing in Design and Manufacture, 3rd Int. Conf.,
   pp. 21--24, PEDC, Dartington (1998)

\bibitem{PolynkinToropov2012}
Polynkin, A. Toropov, V.:
\newblock Mid-range metamodel assembly building based on linear regression for large scale optimization problems.
\newblock Structural and Multidisciplinary Optimization \textbf{45}(4), 515--527 (2012)

\bibitem{LancasterSalkauskas1981}
Lancaster, P. Salkauskas, K.:
\newblock Surfaces generated by moving least squares methods.
\newblock Mathematics of Computation \textbf{87}, 141--158 (1981)

\bibitem{Liszka1984}
Liszka, T.:
\newblock An interpolation method for an irregular net of nodes.
\newblock Int. J. Num. Meth. \textbf{20}, 1599--1612 (1984)

\bibitem{ChoiYounYang2001}
Choi, K., Youn, B., Yang, R.-J.:
\newblock Moving least squares method for reliability-based design optimization.
\newblock In: 4th World Congress of Structural and Multidisciplinary Optimization, Dalian, China (2001)

\bibitem{ToropovSchrammSahaiJones2005}
Toropov, V., Schramm, U., Sahai, A., Jones, R., Zeguer, T.:
\newblock Design optimization and stochastic analysis based on the moving least squares method.
\newblock In: Herskovits, J., Mazorche, S., Canelas, A. (eds.) 6th World Congress of Structural and Multidisciplinary Optimization, art. no. 9412 (2005)

\bibitem{PolynkinToropov2010}
Polynkin, A. Toropov, V.:
\newblock Recognition of design variable inter-dependencies using  cross-validated moving least-squares method.
\newblock In: Proceedings of the 51st AIAA/ASME/ASCE/AHS/ASC Structures, Structural Dynamics, and Materials Conference, AIAA, art. no. 2010-2985 (2010)

\bibitem{OllarToropovJones2014}
Ollar, J., Toropov, V., Jones. R.:
\newblock  Mid-range approximations in sub-spaces for MDO problems with disparate discipline attributes.
\newblock In: 15th AIAA/ISSMO Multidisciplinary Analysis and Optimization Conference, AIAA, art. no. 2014-2437 (2014)

\bibitem{KochYangGu2004}
Koch, P.~N., Yang, R.-J., Gu, L.:
\newblock Design for six sigma through robust optimization.
\newblock Structural and Multidisciplinary Optimization \textbf{26}, 235--248 (2004)

\bibitem{Yao2011}
Yao, W.:
\newblock Review of uncertainty-based multidisciplinary design optimization methods for aerospace vehicles.
\newblock Progress in Aerospace Sciences \textbf {47}, 450--479 (2011)

\bibitem{ZhangZhuChenArendt2013}
Zhang, S., Zhu, P., Chen, W., Arendt, P.:
\newblock Concurrent treatment of parametric uncertainty and metamodeling uncertainty in robust design.
\newblock Structural and Multidisciplinary Optimization \textbf {47}(1), 63--76 (2013)

\bibitem{AouesChateauneuf2010}
Aoues, Y., Chateauneuf, A.:
\newblock Benchmark study of numerical methods for reliability-based design optimization.
\newblock Structural and Multidisciplinary Optimization \textbf {41}(2), 277--294 (2010)

\bibitem{YounChoi2004}
Youn, B.~D., Choi, K.~K.:
\newblock Selecting probabilistic approaches for reliability-based design optimization.
\newblock AIAA journal \textbf{42}(1), 124--131 (2004)

\bibitem{RockafellarRoyset2010}
Rockafellar, R., Royset, J.:
\newblock On buffered failure probability in design and optimization of structures.
\newblock Reliability Engineering \& System Safety \textbf{95}(5), 499--510 (2010)

\bibitem{BasovaRockafellarRoyset}
Basova, H., Rockafellar, R., Royset, J.:
\newblock A computational study of buffered failure probability in reliability-based optimization.
\newblock In: Proceedings of the 11th International Conference on Application of Statistics and Probability in Civil Engineering, Zurich, Switzerland (2011)

\bibitem{RockafellarRoyset2015}
Rockafellar, R.~T., Royset, J.:
\newblock Engineering decisions under risk-averseness.
\newblock ASCE-ASME Journal of Risk and Uncertainty in Engineering Systems, Part A: Civil Engineering
 \textbf{1}(2), art. no. 04015003 (2015)

\bibitem{Caflisch1998}
Caflisch, R.:
\newblock Monte Carlo and quasi-Monte Carlo methods.
\newblock Acta Numerica \textbf{7}, 1--49 (1998)

\bibitem{Niederreiter1992}
Niederreiter, H.:
\newblock Random Number Generation and Quasi-Monte Carlo Methods
\newblock SIAM (1992)

\bibitem{Vanderpllaats2001}
Vanderplaats, G.:
\newblock Multidiscipline Design Optimization. 
\newblock Vanderplaats Research \& Development, Inc., Colorado Springs, (2001)

\end{thebibliography}
